% Make sure to keep the text within the brackets and the output should turn out correct
\acknowledge{%

Over the past 5 years, there has been many constants and many changes, soon
there will be only changes.  Though through it all, I have been surrounded by
wonderful people who have helped and encouraged me to succeed and can only hope
that the relationship was beneficial for them as well.  To begin naming names,
I will begin with my advisor, Professor Renato Figueiredo.  I greatly
appreciate the time he has invested into me and his wisdom shared with me.  I
am greatly blessed to have worked so closely with a professor whom I work so
well with.  That leads me into Professor P. Oscar Boykin, the other head of the
ACIS P2P Group, who along with Professor Figueiredo, molded me into the bold
Ph.D. I am today.  Professor Boykin also helped enrich my design and
development skills, for which, I am extremely grateful.  Rounding out the ACIS
professors, leads to Professor Jose Fortes, who has always been a good source
of wisdom and encouragement.  As leader of the ACIS lab, Professor Fortes has
always been very generous in providing both his time, which is why I am very
appreciative to have him as a member on my Ph.D. committee.  I would also like
thank Professors Shigang Chen and Y. Peter Sheng for their time investments in
my research and whose comments have been invaluable in shaping my dissertation.

My peers and family have also been critical sources of support, encouragement,
and wisdom.  I am thankful to the members of the ACIS P2P group, both past and
present, namely, Tae Woong Choi, Heung Sik Eom, Arijit Ganguly, Kyungyong Lee,
Yonggang Liu, Pierre St. Juste, and Jiangyan Xu, whose comments and
contributions have paved the way for my research.  I am thankful to members of
my sports groups, both the Larsen-Benton Basketball Association and the
Badminton Group for their friendships, as they provided a means to redirect
frustrations developed along the way.  I appreciate the hard work and
dedication of my fellow Archer colleague, Girish Venkatasubramanian.  My
gratitude goes to the kind office ladies who assisted me so much, Catherine
Reeves, Janet Sloan, and Dina Stoeber. I am thankful for the time put forth by
my Grid Appliance colleagues, Panoat Chuchaisri and Arjun Prakash.  My lab
experience would have been much more difficult without the expertise and
kindness of Sumalatha Adabala, Matthew Collins, Andrea Matsunaga, and Mauricio
Tsugawa.  I would like to thank Priya Bhatt, Bingyi Cao, Xin Fu, Selvi
Kadrivel, and Prapaporn Rattanatamrong for their kind hearts and encouragement
and, in some cases, their spicy food.  I would like to thank Donna for her
support and encouragement throughout the years, likewise, I have been blessed
to have parents that have encouraged me to press forward and achieve my goals
in life.

Research is a collaborative effort that, for me at least, involves both
professional and home life.  My success has largely been the result of the
quality individuals that I have been fortunate enough to have in my life.  It
is for those already mentioned and those remembered that this dissertation is
owed.  Thank you so much.
}
