%If you have a single appendix, you need to change {\chapter*{APPENDIX: THIS IS THE FIRST APPENDIX}
%to {\chapter*{APPENDIX: YOUR APPENDIX TITLE HERE} if you have two or more appendices
%you need to change {\chapter{THIS IS THE FIRST APPENDIX}} to
%{\chapter{YOUR APPENDIX TITLE HERE}}
%
%If you make these changes correctly Latex will complain bitterly about the additions to the TOC
%but will make them correctly in a manner acceptable to the Editorial Office.

\ifthenelse{\value{noa} = 1}
%...................then
{\chapter*{APPENDIX: EVALUATION TOOLS}
\label{evaluation_tools}
\addcontentsline{toc}{chapter}{APPENDIX: EVALUATION TOOLS}
\chaptermark{Appendix}
\markboth{Appendix}{Appendix}
\setcounter{chapter}{1}}
%...................else
{\chapter{EVALUATION TOOLS}
\label{evaluation_tools}}
%...................

Netperf~\cite{netperf} is used to estimate the latency and bandwidth of the
different VN models. The latency is measured by deploying Netperf in the
TCP\_RR mode, which measures the number of 1-byte request-receive transactions
that can be completed in a second. The bandwidh is estimated by running Netperf
in the TCP\_STREAM mode, which is a bulk transfer mode. It should be noted that
in situations where the link bandwidths were asymetric, Netperf is deployed in
both directions.  Since both latency and bandwidth are dependent on the CPU
comparison, evaluations that include CPU utilization tasks require creating
a baseline first where only Netperf is the only active workload.

SPECjbb~\cite{specjbb} simulates a three-tier web application with all the
clients, the middle tier, and the database running on a single system in a
single address space (inside a JVM). On completion, the benchmark provides the
metric in terms of business of operations per second (bops). The bops score of
the system under test depends on both the CPU and the memory in the system, as
the entire database for the benchmark is held in memory. This benchmark
generates negligible disk activity and no network activity. 
