% Just type your bio in between the brackets
\biography{%

David Isaac Wolinsky was born on October 31, 1982.  He was blessed with an
awesome, Isaac Emmanuel, born November 30, 2009.  Beginning his studies in
August 2001 at the University of Florida, David obtained the following degrees
in electrical and computer engineering: Bachelor of Science in Spring 2005,
Master of Science in Spring 2007, and Doctorate of Philosophy in Spring 2011.
His advisor at the University of Florida was Professor Renato Figueiredo, whom
he began working with since the during the Spring of 2006 at the Advanced
Computing and Information Systems Lab.

His primary research focuses are network virtualization using structured P2P
overlays and grid computing.  The networking research has been realized in
IPOP, a free (BSD) network virtualization software.  Additionally, he has
worked on enabling DHTs, decentralized NAT traversal through relays, software
models for improved network virtualization, and autonomic virtual networking
stacks.  This work is a major contribution to his grid computing research
focus, Grid Appliance, which enables the creation of decentralized, distributed
grids using virtualized, physical, and cloud resources.  Going forward, he
expressed great interested in using these concepts in other distributed systems
such as sensor networks, social networks, cloud services, or even web services.

During his free time, he enjoys time with my boy, running, playing basketball,
and occasionally playing video games.  At one point, he was ranked in the top
20 on the US East Warcraft III Free For All Ladder.  Most of his time up to
this point has been split between the Archer project and attempting to finish
his Ph.D, which he proudly did before turning 30.  Moving forward, he plans to
research the concept known as hobbies and hopes to have a good time as a
result.

}
